\documentclass{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{biblatex}
\usepackage{csquotes}
\addbibresource{references.bib}
\setlength{\parindent}{0em}
\setlength{\parskip}{1em}


\title{ENGG 683 - Winter 2022\\ Assignment 1}
\author{Bhavyai Gupta}
\date{}


\begin{document}
\maketitle

\section{Part I}

\subsection{The team is developed from diverse groups}

The given statement describes a good team.

\paragraph{Reasons}

\begin{enumerate}
\item Team members with diverse backgrounds brings diverse solutions to the table, which leads to a more informed decision-making process and improved results \cite{diversityBenefits}.

\item Diversity within the team will boost its reputation and help the start-up or the company attract better talent. Businesses that are seen to build and promote diversity in the workplace are viewed as more ethical and socially responsible \cite{diversityBenefits}.
\end{enumerate}

\paragraph{Example}
Accenture has long been known for embracing diversity as a source of innovation, creativity, and competitive advantage. As one of the first tech companies to share its workforce demographics and progress toward internal diversity goals, leadership is holding the company accountable in a very public way. According to Accenture’s latest available data, the company is well on its way to achieving a dynamic workforce that’s highly inclusive of various racial and ethnic backgrounds as well as veterans, military spouses, and persons with disabilities \cite{accentureDemographics}.

\subsection{Issues are expressed freely with the team}

The given statement describes a good team.

\paragraph{Reasons}

\begin{enumerate}
\item It encourages open-communication in the workplace, which leads to a more engaged and trusting team of employees.

\item By acknowledging the issues and working on them, the team can build a better workplace for everyone. This will boost the feeling of inclusion among all the team members, leading to better performance of the individuals and the entire team.
\end{enumerate}

\paragraph{Example}
If underlying issues are not freely expressed with the team, those issues can get aggravated which may lead more troubles in the future. An example of this Facebook. The company is known to ignore red flags raised by its employees, and continue to spread misinformation. The result of this is increased mistrust in Facebook \cite{distrustedFacebook}.


\section{Part II}

My strengths are the technical skills I possess. I need to eliminate doubts over my strengths.

I plan to do so by working on more open-source projects, which will reinforce my skill-set. I also need to take part in more competitions - like hackathons, which will further boost my confidence in myself.

\printbibliography

\end{document}
